\textbf{Discovery of a disrupting open cluster in the Galactic halo:\\ a recent star formation event in the leading arm of the Magellanic stream}

### 2018-11-02 ms.tex
things

We have used the new Gaia data to detect a young, metal-poor cluster in the halo of the Milky Way at a distance of 25 kpc and a MW z-height of 12 kpc.  The detection of such a young cluster so far from the star-forming disks of any nearby
galaxy is highly unusual.  However, the proximity of the new cluster to the Leading Arm of the Magellanic Stream suggests
that the cluster originated from this metal-poor gas \citep{Fox:2018}.  Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, MoniBidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.

@@

>>>>

At the sky location and distance of \clustername, i.e. well into the Galactic halo, the only plausible gas reservoirs that could have formed a young cluster are the Magellanic Stream, or a previously unknown high velocity cloud (HVC).
HVCs are thought to either be accreted and therefore lower metallicity than typical present-day Milky Way gas, or ejected from the Milky Way through a ``Galactic fountain''-like process and therefore comparable metallicity to disk gas.
Both processes clearly occur: the Magellanic Stream itself is evidence of gas accretion in to the Milky Way halo, and the well-known Smith Cloud \citep{TODO} is a metal-rich ($\feh \sim 0.5$), HVC that could have originated from the Galactic disk \citep{TODO}.

Given the low metallicity of the stars in \clustername, the gas it formed from was likely extragalactic, as any violent star-forming regions in the Milky Way disk have, at present-day, significantly higher metallicity than this cluster.
\figurename~\ref{fig:XXXX} shows the \hi column density in the region around the leading arm of the Magellanic Stream, with the location of \clustername\ marked.
While no bulk metallicity measurements exist for the LA gas, \todo{...recent measurements suggest comparable to SMC?} \citep{Fox:2018}.
Given its extragalactic origin, its proximity to the Magellanic Stream suggests that \clustername\ could have formed from this gas.
Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, MoniBidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.

\todo{which gas feature? discuss longitude vs. vlsr}

@@

\todo{Assume velocity, get orbit. Lower energy than LMC, but expected if dissipated during star formation? How much orbital energy lost? Give orbital parameters at midplane.}
